Phenotypic evolution is less constrained in complex food webs or Food-web complexity alters the fitness landscape of an insect herbivore

### 2018-09-21 temporary_morgue/ms_complexity_selection.Rmd
getting organized

@@

## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
complex_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
complex_mean_fitness <- mean(complex_predict)

@@

```{r Code Chunk to demonstrate use of latex2exp package, include=FALSE}
p<-ggplot(data=x, aes(x=y, y=x)) +
geom_errorbar(aes(ymin=x-ci, ymax=x+ci)) +
scale_x_discrete(breaks=c("label1","label2"),
               labels = lapply(sprintf('$\\alpha^\\beta$'), TeX)
p
```

@@

Would we expect any confounding effects on nonlinear selection?
```{r Confounding effects of parasitism on gall size}
## paired t-test approach. Weakness is that it only calculates the selection differential rather than the gradient, which is more meaningful for multivariate trait evolution
pair_df <- gall_selection.df %>%
  group_by(Foodweb, Gall_Number) %>%
  mutate(mean_survival = mean(gall_survival)) %>%
  filter(mean_survival > 0, mean_survival < 1) %>%
  select(Foodweb, Gall_Number, mean_survival, gall_survival, sc.Diam) %>%
  # calculate mean phenotype at gall level (before selection)
  mutate(all_mean_sc.Diam = mean(sc.Diam)) %>%
  # then filter surviving galls and calculate the mean phenotype (after selection)
  filter(gall_survival == 1) %>%
  mutate(survive_mean_sc.Diam = mean(sc.Diam)) %>%
  # only retain distinct data points and calculate the difference (selection differential)
  distinct(Foodweb, Gall_Number, all_mean_sc.Diam, survive_mean_sc.Diam) %>%
  mutate(diff_sc.Diam = survive_mean_sc.Diam - all_mean_sc.Diam)
t.test(diff_sc.Diam ~ Foodweb, pair_df)
t.test(pair_df$survive_mean_sc.Diam, pair_df$all_mean_sc.Diam, paired = T)

@@

Appears to be selection for Platygaster to attack larva at high densities in more complex food webs (and a decrease in the variance). This may be a result of the poorer searching ability of parasitoids at very high gall densities, potentially due to saturation. This suggests that the fitness landscape may be dynamic because these selective effects (assuming there is heritable variation in the egg parasitoid) will change the following year. This could be an important discussion point to take into account for future work. This is different from simply altering the strength of selection, which will occur as species move along the fitness landscape, but this result suggests that the nature of the fitness landscape may actually be changing. For example, larval parasitoids could be driving selection on Platygaster to be very efficient at foraging, which will dampen once this pressure is removed, and then could also dampen the selection acting on the galling herbivore.
```{r Selection on Platygaster Traits}
platy_selection_df <- gall_selection.df %>%
  filter(egg_parasitoid > 0) 
platy_selection_df$Foodweb <- relevel(factor(platy_selection_df$Foodweb), ref = "Simple") # this represents the baseline or absence of selection by larval parasitoids

@@

```{r DUPLICATE for bootstrap test}

## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
complex_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
complex_mean_fitness <- mean(complex_predict)

# test whether using alternative models influences estimes of mean "brackets" and mean fitness 
alt_predict <- predict(foodweb_glmer_2, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
alt_mean_fitness <- mean(alt_predict)
complex_mean_brackets - alt_mean_brackets
complex_mean_fitness - alt_mean_fitness

foodweb_tidy_4 <- filter(tidy(bootMer(foodweb_glmer_4, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T), term %in% c("(Intercept)","FoodwebSimple"))
foodweb_tidy_3 <- filter(tidy(bootMer(foodweb_glmer_3, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T), 
                         term %in% c("sc.Diam","sc.log.Clutch","sc.log1p.Pref",
                                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"))
foodweb_tidy_2 <- filter(tidy(bootMer(foodweb_glmer_2, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T), 
                         term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
                                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"))
foodweb_tidy <- filter(tidy(bootMer(foodweb_glmer, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T), 
                       term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
                                   "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
                                   "sc.Diam:sc.log.Clutch:sc.log1p.Pref",
                                   "FoodwebSimple:sc.Diam:sc.log.Clutch:sc.log1p.Pref"))
## These alphas aren't the appropriate comparison, this is because when there is no interaction term, then the average is taken across all of the food webs. This is okay for testing the statistical significance, but not appropriate when I want to actually compare the magnitudes of the alphas and betas
#foodweb_tidy_4 <- filter(tidy(foodweb_glmer_4), term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref"))
#foodweb_tidy_3 <- filter(tidy(foodweb_glmer_3), term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"))
#foodweb_tidy_2 <- filter(tidy(foodweb_glmer_2), term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"))
#foodweb_tidy <- filter(tidy(foodweb_glmer), term %in% c("FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)","FoodwebSimple:sc.Diam:sc.log.Clutch:sc.log1p.Pref"))

get_alphas <- bind_rows(foodweb_tidy_4, foodweb_tidy_3, foodweb_tidy_2, foodweb_tidy) %>% 
  mutate(alpha = round(statistic, 3), alpha_2.5 = round(conf.low, 3), alpha_97.5 = round(conf.high, 3)) %>%
  select(term, alpha, alpha_2.5, alpha_97.5)

# remember that the selection gradients need to be multiplied by 2 for quadratic gradients.
coefs_gradients <- data.frame(Variable = complex_alphas$term, 
           a_complex = complex_alphas$alpha,
           a_complex_2.5 = complex_alphas$alpha_2.5,
           a_complex_97.5 = complex_alphas$alpha_97.5,
           a_simple = complex_alphas$alpha + simple_alphas$alpha,        # the baseline is the coefficient in the complex food web, therefore we simply add the corresponding coefficients from the simple food web to get the coefficients on the same scale as the complex web
           a_simple_2.5 = complex_alphas$alpha + simple_alphas$alpha_2.5, # same addition process for confidence intervals
           a_simple_97.5 = complex_alphas$alpha + simple_alphas$alpha_97.5) %>% 
  mutate(b_complex = round(complex_mean_brackets * a_complex / complex_mean_fitness, 3),
         b_complex_2.5 = round(complex_mean_brackets * a_complex_2.5 / complex_mean_fitness, 3),
         b_complex_97.5 = round(complex_mean_brackets * a_complex_97.5 / complex_mean_fitness, 3),
         b_simple = round(simple_mean_brackets * a_simple / simple_mean_fitness, 3),
         b_simple_2.5 = round(simple_mean_brackets * a_simple_2.5 / simple_mean_fitness, 3),
         b_simple_97.5 = round(simple_mean_brackets * a_simple_97.5 / simple_mean_fitness, 3))

bind_rows(mutate(select(coefs_gradients, Variable, a=a_complex, a_2.5=a_complex_2.5, a_97.5=a_complex_97.5), Foodweb = "Complex"),
          mutate(select(coefs_gradients, Variable, a=a_simple, a_2.5=a_simple_2.5, a_97.5=a_simple_97.5), Foodweb = "Simple")) %>%
  filter(Variable != "(Intercept)") %>%
  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
  geom_point(aes(y=a), position = position_dodge(width=0.5)) +
  geom_errorbar(aes(ymax = a_97.5, ymin = a_2.5), position = position_dodge(width=0.5)) +
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted")

bind_rows(mutate(select(coefs_gradients, Variable, b=b_complex, b_2.5=b_complex_2.5, b_97.5=b_complex_97.5), Foodweb = "Complex"),
          mutate(select(coefs_gradients, Variable, b=b_simple, b_2.5=b_simple_2.5, b_97.5=b_simple_97.5), Foodweb = "Simple")) %>%
  filter(Variable != "(Intercept)") %>%
  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
  geom_point(aes(y=b), position = position_dodge(width=0.5)) +
  geom_errorbar(aes(ymax = b_97.5, ymin = b_2.5), position = position_dodge(width=0.5)) +
  coord_flip() +
  geom_hline(yintercept=0, linetype="dotted")

@@

```{r Slope and Curvature of Fitness Landscape, include=FALSE}
betas <- c(-0.5,-0.5,0.5)
gammas_matrix <- matrix(c(-0.1, 0.0, 0.0,
                          0.0, -0.1, 0.0,
                          0.0, 0.0, -0.1), 
                        nrow=3, byrow=T)

@@

$$\text{Slope}_{complex} = \beta_{complex} = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} = \begin{pmatrix} 0.4 \\ 0 \\ -0.3 \end{pmatrix}$$
$$\text{Slope}_{simple} = \beta_{simple} = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} = \begin{pmatrix} 0.3 \\ -0.2 \\ -0.3 \end{pmatrix}$$
$$\gamma_{complex} = \begin{pmatrix} \gamma_{diam}&& \\ \gamma_{diam,clutch}&\gamma_{clutch}& \\ \gamma_{diam,pref} & \gamma_{clutch,pref} &\gamma_{pref} \end{pmatrix} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&-0.3 \end{pmatrix}$$
$$\gamma_{simple} = \begin{pmatrix} \gamma_{diam}&& \\ \gamma_{diam,clutch}&\gamma_{clutch}& \\ \gamma_{diam,pref} & \gamma_{clutch,pref} &\gamma_{pref} \end{pmatrix} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&0 \end{pmatrix}$$
$$\text{Curvature} = \gamma - \beta \beta^T$$
$$\text{Curvature}_{complex} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&0 \end{pmatrix}$$
$$\text{Curvature}_{simple} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&0 \end{pmatrix}$$

```{r Effects of platy vs. ecto on absolute fitness, cache=TRUE, include=FALSE}

@@

```{r For platy ecto comparison}
## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
complex_predict <- predict(platyecto_glmer, newdata=filter(gall_selection.df, Foodweb == "Complex" & platy < 1), type="response")
complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
complex_mean_fitness <- mean(complex_predict)

@@

```{r}
## Calculating same coefficients as for simple vs. complex food web

@@

Compared to the GLM, the GLMM gives the same inferences about the effect of food-web treatment. The main difference was that there was stronger evidence of correlational selection, but no evidence that this correlational selection varied among food-web treatments. Still, this stronger evidence for correlational selection should be interpreted with caution since the GLM does not account for the non-indepedence of these fitness estimates. 
```{r Compare GLMM to GLM}
## Fit GLMs. Dispersion parameter was ~1, so I just used a binomial model. 
null_glm <- glm(gall_survival ~ sc.Diam*sc.log.Clutch*sc.log1p.Pref + 
                      I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2),
                    data = gall_selection.df,
                    family = binomial(link = logit))

@@

```{r Get Selection Gradients for GLM}
complex_predict <- predict(foodweb_glm, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
complex_mean_fitness <- mean(complex_predict)

@@

```{r Mortality, include=F}
# 8-10% mortality induced by intraguild predators
mean(control_df$platy)
mean(treatment_df$platy)
mean(eggptoid_control_df$platy)

@@

```{r Figure 1, echo=FALSE, fig.cap="Illustrations of complex (A) and simple (B) food webs associated with the insect herbivore, *Iteomyia salicisverruca*. Black arrows denote 'who-eats-whom' in this network of trophic interactions."}
knitr::include_graphics("complex_simple_foodwebs_compressed.pdf")
```

@@

We found that changes in food-web complexity altered the shape of *Iteomyia*'s fitness landscape ($\chi^2_{`r foodweb_test$[2,"Chi.Df"]`}=`r foodweb_test$[2,"statistic"]`, P=`r foodweb_test$[2,"p.value"]`$).

@@

**Old**
Two key patterns emerged from our analyses. First, fewer phenotypic traits were under selection in the complex vs. simple food web. 
In both complex and simple food webs, gall diameter was under strong directional selection, with larger galls resulting in higher larval survival (complex $\beta_{diam}=$`r paste0(filter(summary_beta_control, Phenotype=="Gall diameter")$Estimate," [",filter(summary_beta_control, Phenotype=="Gall diameter")$lower_2.5,",",filter(summary_beta_control, Phenotype=="Gall diameter")$upper_97.5,"]")`; simple $\beta_{diam}=$ `r paste0(filter(summary_beta_treatment, Phenotype=="Gall diameter")$Estimate," [",filter(summary_beta_treatment, Phenotype=="Gall diameter")$lower_2.5,",",filter(summary_beta_treatment, Phenotype=="Gall diameter")$upper_97.5,"]")`)(Fig. \ref{fig:Univariate_Landscapes}A).

@@

```{r Get Gall Diameter Relative Fitness Landscape, include=FALSE, cache=TRUE}

@@

```{r Get Clutch Size Fitness Landscape, include=FALSE, cache=TRUE}

@@

```{r Get Female Preference Fitness Landscape, include=FALSE, cache=TRUE}

@@

```{r Get Clutch Size x Female Preference Landscape, include=FALSE, cache=TRUE}

@@

```{r Get Gall Diameter x Clutch Size Landscape, include=FALSE, cache=TRUE}

@@

```{r Get Gall Diameter x Female Preference Landscape, include=FALSE, cache=TRUE}

@@

```{r Fitness Landscape Plot Helpers, include=FALSE, cache=TRUE}

@@

```{r Plot Univariate Landscapes, include=FALSE, cache=TRUE}
uni_breaks <- c(0.1,0.5,1)

@@

```{r Univariate_Landscapes, echo=FALSE, fig.cap="\\label{fig:Univariate_Landscapes}Selection gradients acting on gall traits in complex vs. simple food webs. Each panel corresponds to a different gall trait: gall diameter (A); clutch size (B); and female preference (C). Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs. Transparent lines represent bootstrapped replicates (n=100) to show the uncertainty in estimated gradients. Note that only 100 bootstraps are displayed here, but that inferences are based on 1,000 bootstrapped samples."}

@@

```{r Plot Multivariate Fitness Landscape, include=FALSE, cache=TRUE}

@@

```{r Multivariate_Landscapes, echo=FALSE, fig.cap="\\label{fig:Multivariate_Landscapes}Fitness landscapes of gall traits in complex vs. simple food webs. Each panel corresponds to a different combination of traits: clutch size and gall diameter (A); clutch size and female preference (B); female preference and gall diameter (C). Note that traits for all plots range 1 SD below and above the mean (=0)."}
# Get legend
AF_landscape_legend <- get_legend(AF_plot_size.x.preference)

@@

```{r AIC Model Comparison, include=FALSE, cache=TRUE}

# Control ----
AIC(beta_control, quad_control, corr_control)

glm.beta_control <- glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data=control_df, family=binomial(link=logit))

beta_control.REonlyGallID <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
                                   (1|Gall_Number),
                                 data = control_df,
                                 family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

AIC(beta_control, glm.beta_control)
AIC(beta_control, beta_control.REonlyGallID)
overdisp_fun(beta_control)

# Treatment ----
AIC(beta_treatment, quad_treatment, corr_treatment)

glm.beta_treatment <- glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data=treatment_df, family=binomial(link=logit))

beta_treatment.REonlyGallID <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
                                   (1|Genotype/Plant_Position),
                                 data = treatment_df,
                                 family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))

overdisp_fun(beta_treatment)

AIC(beta_treatment, glm.beta_treatment)
AIC(beta_treatment, beta_treatment.REonlyGallID)
anova(beta_treatment, beta_treatment.REonlyGallID)
anova(beta_treatment, glm.beta_treatment)
```

@@

```{r Univariate Absolute Fitness Landscapes, include=FALSE}
## Absolute fitness plots ----

@@

```{r Figure S1 Univariate Absolute Fitness Landscapes, include=FALSE}

@@

```{r Multivariate Absolute Fitness Landscapes, include=FALSE}

@@

```{r Figure S2 Multivariate Absolute Fitness Landscapes, include=FALSE}
# Get legend
AF_landscape_legend <- get_legend(AF_plot_size.x.preference)

@@

```{r OLD GAMM comparison, eval=FALSE, include=FALSE}
gamm_control <- gamm.model(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
                         I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
                         sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference, 
                         data = control_df)
summary(gamm_control$gam)

gam.gradients(gamm_control$gam, phenotype=c("sc.gall_size","sc.log.clutch_size"), covariates = c("sc.log1p.female_preference"), se.method="none")
gam.gradients(gamm_control$gam, phenotype=c("sc.gall_size","sc.log1p.female_preference"), covariates = c("sc.log.clutch_size"), se.method="none")
gam.gradients(gamm_control$gam, phenotype=c("sc.log.clutch_size","sc.log1p.female_preference"), covariates = c("sc.gall_size"), se.method="none")

AIC(corr_control, gamm_control$mer)
```

```{r OLD Selection Gradients - Complex Food Web, eval=FALSE, include=FALSE}
# note that I've switched to using the lme4 package to analyzing the GLMM

# GLMM ----
glmer_control <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
                         I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
                         sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference +
                           (1|Genotype/Plant_Position/Gall_Number),
                         data = control_df,
                         family = binomial(link = logit), optimizer = "bobyqa")
summary(glmer_control)

# Mean fitness ----
Wbar_control <- inverse_logit(fixef(update(glmer_control, .~. -sc.gall_size -sc.log.clutch_size -sc.log1p.female_preference)))

# Confidence intervals for selection gradients ----
boot_Beta_control <- bootMer(glmer_control, FUN = Beta_avg_grad, nsim=100, parallel="multicore", ncpus=32)

## Summary ----
summary_Beta_glmm_control <- data.frame(
  Phenotype = c("Gall size", "Clutch size", "Female preference"),
  Food_Web = "Complex",
  Model = "GLMM",
  Beta = round(Beta_avg_grad(glmer_control),3),
  lower_2.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
  upper_97.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))

summary_Beta_glmm_control
```

```{r Get 3D, include=FALSE, eval=FALSE}
# note that length.out=10 now
library(FD)

# Control ----
RF_control_3D <- bootstrap_fitness(
  logistic_model = beta_control, 
  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference",
  newdata = expand.grid(
     sc.gall_size = seq(-1,1,length.out=10),
     sc.log.clutch_size = seq(-1,1,length.out=10),
     sc.log1p.female_preference = seq(-1,1,length.out=10)), 
  bootstraps=NULL)
mean(RF_control_3D$relative_fitness$average)

control_traits <- RF_control_3D$relative_fitness %>%
  filter(average < 1) %>%
  select(-average) %>%
  mutate(Treatment = "Control")

FD_control <- dbFD(control_traits)

FD_control

# Treatment ----
RF_treatment_3D <- bootstrap_fitness(
  logistic_model = beta_treatment, 
  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference",
  newdata = expand.grid(
     sc.gall_size = seq(-1,1,length.out=10),
     sc.log.clutch_size = seq(-1,1,length.out=10),
     sc.log1p.female_preference = seq(-1,1,length.out=10)), 
  bootstraps=NULL)
mean(RF_treatment_3D$relative_fitness$average)

>>>>

```{r Model Modification}

# In terms of the gammas, there was only evidence that food-web treatment altered nonlinear selection on preference
summary(foodweb_glmer)

# Therefore, we refit a model that only included this effect of food-web treatment on the gamma coefficients
foodweb_glmer_revised <- update(foodweb_glmer, .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)

# Note that we still observe that food-web treatment alters nonlinear selection on female preference
# There is also now marginal evidence for nonlinear selection on diameter as well as correlational selection between diameter and clutch (Diam:Clutch) and between diameter and preference (Diam:Pref).
summary(foodweb_glmer_revised)

summary(betas_glmer)

betas_glmer_revised <- update(betas_glmer, .~. -Foodweb:sc.Diam -Foodweb:sc.log1p.Pref)
summary(betas_glmer_revised)

foodweb_glmer_revised_again <- update(foodweb_glmer_revised, .~. -Foodweb:sc.Diam -Foodweb:sc.log1p.Pref)
summary(foodweb_glmer_revised_again)
```

@@

```{r Parametric Bootstrapping of Regression Coefficients and Selection Gradients, cache=TRUE, include=FALSE}

## DUPLICATE ABOVE EXCEPT MODIFY FOR BOOTMER

@@

```{r Code Chunk to demonstrate use of latex2exp package, include=FALSE, eval=FALSE}
## NOT WORKING

library(latex2exp)
data.frame(x=1:10,y=1:10)
p<-ggplot(data=x, aes(x=y, y=x)) +
geom_errorbar(aes(ymin=x-ci, ymax=x+ci)) +
scale_x_discrete(breaks=c("label1","label2"),
               labels = lapply(sprintf('$\\alpha^\\beta$'), TeX)
p
```

@@

Would we expect any confounding effects on nonlinear selection?
```{r Confounding effects of parasitism on gall size, include=FALSE, eval=FALSE}
## paired t-test approach. Weakness is that it only calculates the selection differential rather than the gradient, which is more meaningful for multivariate trait evolution
pair_df <- gall_selection.df %>%
  group_by(Foodweb, Gall_Number) %>%
  mutate(mean_survival = mean(gall_survival)) %>%
  filter(mean_survival > 0, mean_survival < 1) %>%
  select(Foodweb, Gall_Number, mean_survival, gall_survival, sc.Diam) %>%
  # calculate mean phenotype at gall level (before selection)
  mutate(all_mean_sc.Diam = mean(sc.Diam)) %>%
  # then filter surviving galls and calculate the mean phenotype (after selection)
  filter(gall_survival == 1) %>%
  mutate(survive_mean_sc.Diam = mean(sc.Diam)) %>%
  # only retain distinct data points and calculate the difference (selection differential)
  distinct(Foodweb, Gall_Number, all_mean_sc.Diam, survive_mean_sc.Diam) %>%
  mutate(diff_sc.Diam = survive_mean_sc.Diam - all_mean_sc.Diam)
t.test(diff_sc.Diam ~ Foodweb, pair_df)
t.test(pair_df$survive_mean_sc.Diam, pair_df$all_mean_sc.Diam, paired = T)

@@

Appears to be selection for Platygaster to attack larva at high densities in more complex food webs (and a decrease in the variance). This may be a result of the poorer searching ability of parasitoids at very high gall densities, potentially due to saturation. This suggests that the fitness landscape may be dynamic because these selective effects (assuming there is heritable variation in the egg parasitoid) will change the following year. This could be an important discussion point to take into account for future work. This is different from simply altering the strength of selection, which will occur as species move along the fitness landscape, but this result suggests that the nature of the fitness landscape may actually be changing. For example, larval parasitoids could be driving selection on Platygaster to be very efficient at foraging, which will dampen once this pressure is removed, and then could also dampen the selection acting on the galling herbivore.
```{r Selection on Platygaster Traits, include=FALSE, eval=FALSE}
platy_selection_df <- gall_selection.df %>%
  filter(egg_parasitoid > 0) 
platy_selection_df$Foodweb <- relevel(factor(platy_selection_df$Foodweb), ref = "Simple") # this represents the baseline or absence of selection by larval parasitoids

@@

@@

```{r Slope and Curvature of Fitness Landscape, include=FALSE, eval=FALSE}
betas <- c(-0.5,-0.5,0.5)
gammas_matrix <- matrix(c(-0.1, 0.0, 0.0,
                          0.0, -0.1, 0.0,
                          0.0, 0.0, -0.1), 
                        nrow=3, byrow=T)

@@

```{r LATEX NEED TO CHECK, eval=FALSE, include=FALSE}
$$\text{Slope}_{complex} = \beta_{complex} = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} = \begin{pmatrix} 0.4 \\ 0 \\ -0.3 \end{pmatrix}$$
$$\text{Slope}_{simple} = \beta_{simple} = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} = \begin{pmatrix} 0.3 \\ -0.2 \\ -0.3 \end{pmatrix}$$
$$\gamma_{complex} = \begin{pmatrix} \gamma_{diam}&& \\ \gamma_{diam,clutch}&\gamma_{clutch}& \\ \gamma_{diam,pref} & \gamma_{clutch,pref} &\gamma_{pref} \end{pmatrix} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&-0.3 \end{pmatrix}$$
$$\gamma_{simple} = \begin{pmatrix} \gamma_{diam}&& \\ \gamma_{diam,clutch}&\gamma_{clutch}& \\ \gamma_{diam,pref} & \gamma_{clutch,pref} &\gamma_{pref} \end{pmatrix} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&0 \end{pmatrix}$$
$$\text{Curvature} = \gamma - \beta \beta^T$$
$$\text{Curvature}_{complex} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&0 \end{pmatrix}$$
$$\text{Curvature}_{simple} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&0 \end{pmatrix}$$
```

```{r Effects of platy vs. ecto on absolute fitness, cache=TRUE, include=FALSE, eval=FALSE}

@@

```{r For platy ecto comparison, include=FALSE, eval=FALSE}
## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
complex_predict <- predict(platyecto_glmer, newdata=filter(gall_selection.df, Foodweb == "Complex" & platy < 1), type="response")
complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
complex_mean_fitness <- mean(complex_predict)

@@

```{r include=FALSE, eval=FALSE}
## Calculating same coefficients as for simple vs. complex food web

@@

Compared to the GLM, the GLMM gives the same inferences about the effect of food-web treatment. The main difference was that there was stronger evidence of correlational selection, but no evidence that this correlational selection varied among food-web treatments. Still, this stronger evidence for correlational selection should be interpreted with caution since the GLM does not account for the non-indepedence of these fitness estimates. 
```{r Compare GLMM to GLM, include=FALSE, eval=FALSE}
## Fit GLMs. Dispersion parameter was ~1, so I just used a binomial model. 
null_glm <- glm(gall_survival ~ sc.Diam*sc.log.Clutch*sc.log1p.Pref + 
                      I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2),
                    data = gall_selection.df,
                    family = binomial(link = logit))

@@

```{r Get Selection Gradients for GLM, include=FALSE, eval=FALSE}
complex_predict <- predict(foodweb_glm, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
complex_mean_fitness <- mean(complex_predict)

@@

```{r Mortality, include=FALSE, eval=FALSE}
# 8-10% mortality induced by intraguild predators
mean(control_df$platy)
mean(treatment_df$platy)
mean(eggptoid_control_df$platy)

@@

```{r Figure 1, include=FALSE, eval=FALSE, echo=FALSE, fig.cap="Illustrations of complex (A) and simple (B) food webs associated with the insect herbivore, *Iteomyia salicisverruca*. Black arrows denote 'who-eats-whom' in this network of trophic interactions."}
knitr::include_graphics("complex_simple_foodwebs_compressed.pdf")
```

@@

We found that changes in food-web complexity altered the shape of *Iteomyia*'s fitness landscape ().

@@

**Old**

```{r OLD TEXT, include=FALSE, eval=FALSE}
$\chi^2_{`r foodweb_test$[2,"Chi.Df"]`}=`r foodweb_test$[2,"statistic"]`, P=`r foodweb_test$[2,"p.value"]`$).

Two key patterns emerged from our analyses. First, fewer phenotypic traits were under selection in the complex vs. simple food web. 
In both complex and simple food webs, gall diameter was under strong directional selection, with larger galls resulting in higher larval survival (complex $\beta_{diam}=$`r paste0(filter(summary_beta_control, Phenotype=="Gall diameter")$Estimate," [",filter(summary_beta_control, Phenotype=="Gall diameter")$lower_2.5,",",filter(summary_beta_control, Phenotype=="Gall diameter")$upper_97.5,"]")`; simple $\beta_{diam}=$ `r paste0(filter(summary_beta_treatment, Phenotype=="Gall diameter")$Estimate," [",filter(summary_beta_treatment, Phenotype=="Gall diameter")$lower_2.5,",",filter(summary_beta_treatment, Phenotype=="Gall diameter")$upper_97.5,"]")`)(Fig. \ref{fig:Univariate_Landscapes}A).

@@

-->
```

```{r Get Gall Diameter Relative Fitness Landscape, cache=TRUE, include=FALSE, eval=FALSE}

@@

```{r Get Clutch Size Fitness Landscape, cache=TRUE, include=FALSE, eval=FALSE}

@@

```{r Get Female Preference Fitness Landscape, include=FALSE, eval=FALSE}

@@

```{r Get Clutch Size x Female Preference Landscape, include=FALSE, eval=FALSE}

@@

```{r Get Gall Diameter x Clutch Size Landscape, include=FALSE, eval=FALSE}

@@

```{r Get Gall Diameter x Female Preference Landscape, include=FALSE, eval=FALSE}

@@

```{r Fitness Landscape Plot Helpers, include=FALSE, eval=FALSE}

@@

```{r Plot Univariate Landscapes, include=FALSE, eval=FALSE}
uni_breaks <- c(0.1,0.5,1)

@@

```{r Univariate_Landscapes, include=FALSE, eval=FALSE, echo=FALSE, fig.cap="\\label{fig:Univariate_Landscapes}Selection gradients acting on gall traits in complex vs. simple food webs. Each panel corresponds to a different gall trait: gall diameter (A); clutch size (B); and female preference (C). Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs. Transparent lines represent bootstrapped replicates (n=100) to show the uncertainty in estimated gradients. Note that only 100 bootstraps are displayed here, but that inferences are based on 1,000 bootstrapped samples."}

@@

```{r Plot Multivariate Fitness Landscape, include=FALSE, eval=FALSE}

@@

```{r Multivariate_Landscapes, include=FALSE, eval=FALSE, echo=FALSE, fig.cap="\\label{fig:Multivariate_Landscapes}Fitness landscapes of gall traits in complex vs. simple food webs. Each panel corresponds to a different combination of traits: clutch size and gall diameter (A); clutch size and female preference (B); female preference and gall diameter (C). Note that traits for all plots range 1 SD below and above the mean (=0)."}
# Get legend
AF_landscape_legend <- get_legend(AF_plot_size.x.preference)

@@

@@

```{r Univariate Absolute Fitness Landscapes, include=FALSE, eval=FALSE}
## Absolute fitness plots ----

@@

```{r Figure S1 Univariate Absolute Fitness Landscapes, include=FALSE, eval=FALSE}

@@

```{r Multivariate Absolute Fitness Landscapes, include=FALSE, eval=FALSE}

@@

```{r Figure S2 Multivariate Absolute Fitness Landscapes, include=FALSE, eval=FALSE}
# Get legend
AF_landscape_legend <- get_legend(AF_plot_size.x.preference)

@@
